%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Written By Michael Brodskiy
% Class: Cornerstone Engineering 1 & 2 (GE1501 & GE1502)
% Professor: B. O'Connell
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{Includes.tex}

\renewcommand{\labelenumi}{[\arabic{enumi}]}
\hypersetup{
colorlinks=true,
linkcolor=black,
filecolor=black,      
urlcolor=black,
citecolor=black,
}

\title{Researching Educational Exhibits}
\date{\today}
\author{Michael Brodskiy\\ \small Professor: B. O'Connell}

\begin{document}

\maketitle

\begin{enumerate}

  \item “Universal Design for Museum Learning Experiences,” \textit{Museum of Science, Boston}. [Online]. Available: \href{https://www.mos.org/UniversalDesign}{https://www.mos.org/UniversalDesign}. [Accessed: 18-Oct-2022]. 

  \item “EDGE Exhibit Designs for Girls’ Engagement.” Exploratorium.  \\\href{https://www.exploratorium.edu/education/research-evaluation/edge}{https://www.exploratorium.edu/education/research-evaluation/edge} (accessed: Oct. 18, 2022).

  \item “Exhibits | International Spy Museum.” The International Spy Museum.\\ \href{https://www.spymuseum.org/exhibition-experiences/}{https://www.spymuseum.org/exhibition-experiences/} (accessed: Oct. 18, 2022).

  \item “Interactive Exhibits | Creative Machines.” Creative Machines.\\ \href{https://www.creativemachines.com/interactive-exhibits}{https://www.creativemachines.com/interactive-exhibits} (accessed: Oct. 18, 2022).

  \item “Cryptography.” \href{Wikipedia. https://en.wikipedia.org/wiki/Cryptography}{Wikipedia. https://en.wikipedia.org/wiki/Cryptography} (accessed: Oct. 18, 2022).

  \item M. F. Mortensen, “Analysis of the Educational Potential of a Science Museum Learning Environment: Visitors’ experience with and understanding of an immersion exhibit.” \textit{International Journal of Science Education}, vol. 33, no. 4, pp. 517-545, 2010, doi: 10.1080/09500691003754589. 

  \item R. J. Batvinis, ``\textit{Spy Satellites and Other Intelligence Technologies that Changed History}''. By Thomas Graham Jr. and Keith A. Hansen. (Seattle, Wash.: University of Washington, 2007. Pp.ix, 162. \$14.95.).” \textit{The Historian}, vol. 71, no. 1, pp. 111-112, 2009, doi: 10.1111/j.1540-6563.2008.00233\_14.x.

\end{enumerate}

\end{document}

